handover issues in medical care

### 2024-01-21 inst/handover.Rmd
consistentification
fixes #218

---
title: "handover issues in medical care"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a.
This short document is based on @altham2010, which
discussed an interesting dataset originally presented by Lin
et. al. (2009).  It uses more sophisticated idiom furnished by the
`hyper2` package, which is an improved and efficient upgrade of the
primitive `hyperdirichlet` package.  The dataset arose from 69 medical
malpractice claims and refers to the two surgeon–reviewers' answers to
the question "was there a communication breakdown in the hand-off
between physicians caring for the patient?".  The rows of Table 1
correspond to the answers that were given by reviewer 1, and the
columns to the answers given by reviewer 2.

@@

handover[c("t11","t10")] %<>% inc(handover_table[1,3])  # yes-yes plus yes-no  = 2 
handover[c("t01","t00")] %<>% inc(handover_table[2,3])  #  no-yes plus  no-no  = 9 
handover[c("t11","t01")] %<>% inc(handover_table[3,1])  # yes-yes plus  no-yes = 4 
handover[c("t10","t00")] %<>% inc(handover_table[3,2])  # yes-no  plus  no-no  = 4 
handover
handover_maxp <- maxp(handover)
handover_maxp
```

>>>>

---
title: "handover issues in medical care"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017.
This short document is based on @altham2010, which
discussed an interesting dataset originally presented by Lin
et. al. (2009).  It uses more sophisticated idiom furnished by the
`hyper2` package, which is an improved and efficient upgrade of the
primitive `hyperdirichlet` package.  The dataset arose from 69 medical
malpractice claims and refers to the two surgeon–reviewers' answers to
the question "was there a communication breakdown in the hand-off
between physicians caring for the patient?".  The rows of Table 1
correspond to the answers that were given by reviewer 1, and the
columns to the answers given by reviewer 2.

@@

handover[c("t11","t10")] %<>% inc(handover_table[1,3])  # yes-yes plus yes-no  = 2 
handover[c("t01","t00")] %<>% inc(handover_table[2,3])  #  no-yes plus  no-no  = 9 
handover[c("t11","t01")] %<>% inc(handover_table[3,1])  # yes-yes plus  no-yes = 4 
handover[c("t10","t00")] %<>% inc(handover_table[3,2])  # yes-no  plus  no-no  = 4 
handover <- balance(handover)
handover
handover_maxp <- maxp(handover)
handover_maxp
```
